R Notebook

### 2025-01-08 landscapemodels_gam.Rmd
remake site

polplot.df <- plot_fun(pol.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "margin_dens"),
                       wfs_lsm)

@@

residpolplot.df <- plot_fun(polresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

swyplot.df <- plot_fun(swy.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "margin_dens"),
                       wfs_lsm)

@@

residswyplot.df <- plot_fun(swyresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

residndrplot.df <- plot_fun(ndrresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

sdrplot.df <- plot_fun(sdr.gam1, 
                       c("ann_agr_pland", "prn_agr_pland", "margin_dens"),
                       wfs_lsm)

@@

residsdrplot.df <- plot_fun(sdrresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

>>>>

polplot.df <- plot_fun(pol.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "margin_dens", "lu_shdi"),
                       wfs_lsm)

@@

residpolplot.df <- plot_fun(polresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

swyplot.df <- plot_fun(swy.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "margin_dens", "lu_shdi"),
                       wfs_lsm)

@@

residswyplot.df <- plot_fun(swyresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

residndrplot.df <- plot_fun(ndrresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn","lu_shdi"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

@@

sdrplot.df <- plot_fun(sdr.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "margin_dens", "lu_shdi"),
                       wfs_lsm)

@@

residsdrplot.df <- plot_fun(sdrresid.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm_resids,
                       "ann_agr_pland")

### 2025-01-08 landscapemodels_margin.Rmd
remake site

wfs_lsm <- wfs %>% left_join(lsm, by = "hu") %>%
  select(c(hu, huc2, name, margin.ha, lu_ta,
           pollinators_base:sed_export_base, 
           pollinators_max:sed_export_max, 
           delta_pollinators:delta_sed, 
           fields_max, field.ha, margin.ha, 
           lu_shdi:ntr_frac_mn)) %>%
  mutate(prn_ann_ratio = log(prn_agr_pland/ann_agr_pland),
         prn_pagr = 100*(prn_agr_pland/(ann_agr_pland+prn_agr_pland)),
         field_pland = field.ha/lu_ta,
         margin_dens = margin.ha/lu_ta,
         delta_pollinators.margin = delta_pollinators/margin.ha,
         delta_qb.margin = delta_qb/margin.ha,
         delta_n_export.margin = delta_n_export/margin.ha,
         delta_sed.margin = delta_sed/margin.ha)

@@

## Correlation between independent variables.

I selected a subset of variables that aren't strongly correlated and that represent potential drivers of ecosystem service patterns.

```{r correlation, echo = FALSE}

pairs.panels(wfs_lsm %>% 
               select(ann_agr_pland, prn_agr_pland, aglu_iji,
                      lu_shdi, aglu_frac_mn, margin_dens), 
             cex.cor = 1, cex.labels=1, cex=0.5, method = "pearson")

@@

pol.gam1 <- gam(delta_pollinators.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi), 
                data = wfs_lsm)

@@

polplot.df <- plot_fun(pol.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm, "ann_agr_pland")

@@

swy.gam1 <- gam(delta_qb.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi), 
                data = wfs_lsm)

@@

swyplot.df <- plot_fun(swy.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm, "ann_agr_pland")

@@

ndr.gam1 <- gam(delta_n_export.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi), 
                data = wfs_lsm)

@@

ndrplot.df <- plot_fun(ndr.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm, "ann_agr_pland")

@@

sdr.gam1 <- gam(delta_sed.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi), 
                data = wfs_lsm)

@@

sdrplot.df <- plot_fun(sdr.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi"),
                       wfs_lsm, "ann_agr_pland")

>>>>

wfs_lsm <- wfs %>% left_join(lsm, by = "hu") %>%
  select(c(hu, huc2, name, margin.ha, lu_ta,
           pollinators_base:sed_export_base, 
           pollinators_max:sed_export_max, 
           delta_pollinators:delta_sed, 
           fields_max, field.ha, margin.ha, 
           lu_shdi:ntr_frac_mn)) %>%
  mutate(prn_ann_ratio = log(prn_agr_pland/ann_agr_pland),
         prn_pagr = 100*(prn_agr_pland/(ann_agr_pland+prn_agr_pland)),
         field_pland = field.ha/lu_ta,
         margin_dens = margin.ha/lu_ta,
         delta_pollinators.margin = delta_pollinators/margin_dens,
         delta_qb.margin = delta_qb/margin_dens,
         delta_n_export.margin = delta_n_export/margin_dens,
         delta_sed.margin = delta_sed/margin_dens)

@@

## Normalize ecosystem service results by margin

Change in ecosystem service is normalized by hectares of margin added so that the dependent variable is unit ES per area margin instead of per area watershed

@@

pol.gam1 <- gam(delta_pollinators.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi) + s(lu_ta), 
                data = wfs_lsm)

@@

polplot.df <- plot_fun(pol.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi", "lu_ta"),
                       wfs_lsm, "ann_agr_pland")

@@

swy.gam1 <- gam(delta_qb.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi) + s(lu_ta), 
                data = wfs_lsm)

@@

swyplot.df <- plot_fun(swy.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi", "lu_ta"),
                       wfs_lsm, "ann_agr_pland")

@@

ndr.gam1 <- gam(delta_n_export.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi) + s(lu_ta), 
                data = wfs_lsm)

@@

ndrplot.df <- plot_fun(ndr.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi", "lu_ta"),
                       wfs_lsm, "ann_agr_pland")

@@

sdr.gam1 <- gam(delta_sed.margin ~ s(ann_agr_pland) + s(aglu_iji) + s(prn_agr_pland) + s(aglu_frac_mn) + s(lu_shdi) + s(lu_ta), 
                data = wfs_lsm)

@@

sdrplot.df <- plot_fun(sdr.gam1, 
                       c("ann_agr_pland", "aglu_iji", "prn_agr_pland", "aglu_frac_mn", "lu_shdi", "lu_ta"),
                       wfs_lsm, "ann_agr_pland")
